Group Signatures Meet Anonymous Credentials: Or, How to Build Privacy Preserving Identities with Accountability

### 2022-02-17 prism-backend/research/gsac/uas-model.tex
Refining oracles. Some doubts remain; should be solved while specifying games.

  \Obtain(\usk,\uattrs,\dattrs,\ldblbrace (gpk_i,\cred_i,\uattrs_i,\dattrs_i)\rdblbrace_{i \in \Issuers}),
  \Issue(\isk,\upk,\ldblbrace (\gpk_i,\dattrs_i)\rdblbrace_{i \in \Issuers})

@@

  the ones in the $\uattrs_i$'s) are kept hidden from the issuer, while those in
  \dattrs (as well as those in the $\dattrs_i$'s) are revealed. Moreover,
  $\uattrs \cup \dattrs$ must be a subset of $\bigcup_i (\uattrs_i \cup
  \dattrs_i)$. In order to get the credential, the user may leverage previously

@@

  undisclosed attributes $\uattrs_i$. The user
  outputs the produced credential \cred, while the issuer outputs the protocol
  transcript \utrans for the produced credential.
\item[$\sig \gets \Sign(\usk,\ldblbrace (\gpk_i,\cred_i,\uattrs_i,\dattrs_i)
  \rdblbrace_{i \in \Issuers},\msg)$.] %

@@

  $\bigcup_i \uattrs_i$.

@@

  \Verify(\sig,\msg,\ldblbrace (\gpk_i,\dattrs_i) \rdblbrace_{i \in \Issuers})$.]

@@

  arbitrary claims over disclosed attributes $\bigcup_i \dattrs_i$, as well as

@@

  \Inspect(\osk,\utrans,\sig,\msg,
  \ldblbrace (\gpk_i,\dattrs_i) \rdblbrace_{i \in \Issuers})$.] %
  \commentwho{Jesus}{I do not like this definition. It's complicated. This needs

@@

  disclosed attributes $\bigcup_i \dattrs_i$, as well as potentially undisclosed

@@

  If \utrans is a valid transcript of the execution of a

@@

  the credential associated to the inspector's group, then the function outputs

@@

\item[$1/0 \gets \Judge(\y,\iproof,\sig,\msg,
  \ldblbrace (\gpk_i,\dattrs_i)\rdblbrace_{i \in \Issuers})$.] %

@@

\paragraph{Oracles.} %
Oracles are the interface of the adversary with the corresponding games. In
other words: through these oracles, the game environment exposes to the adversary
functionality that could otherwise be executed only by honest parties with
private knowledge -- knowledge that would make the adversary capable of
trivially breaking the security properties formalized in the experiments.
In the game-based definitions of our \GSAC model, we leverage the following
oracles, which are formally defined in \figref{fig:oracles}. Note that we
identify issuers and inspectors by the group identifier.

@@

        \procedure{$\HIGEN(\gid,\fissue)$}{%
          \pcif \gid \in \HI \lor \gid \in \CI: \pcreturn \bot \\
          (\ipk,\isk) \gets \IKeyGen(\parm) \\
          \IK[\gid] \gets (\ipk,\isk,\fissue);
          \HI \gets \HI \cup \lbrace \gid \rbrace \\
          \pcreturn \ipk \\
        }

        \procedure{$\CIGEN(\gid,\ipk,\fissue)$}{%
          \pcif \gid \in \CI: \pcreturn \bot \\
          \CI \gets \CI \cup \lbrace \gid \rbrace \\          
          \pcif \gid \in \HI: \\
          \pcind \HI \gets \HI \setminus \lbrace \gid \rbrace; \\
          \pcind \pcreturn \IK[\gid] \\
          \pcelse: \IK[\gid] = (\ipk,\bot,\fissue) \\          
          \pcreturn \top \\
        }

        \procedure{$\HUGEN(\uid)$}{%
          \pcif \uid \in \HU \lor \uid \in \CU: \pcreturn \bot \\
          (\upk,\usk) \gets \UKeyGen(\parm) \\
          \UK[\uid] \gets (\upk,\usk);
          \HU \gets \HU \cup \lbrace  \uid \rbrace \\
          \pcreturn \top \\
        }

        \procedure{$\ISSUE(\cid,\uid,\gid,
          \lbrace (\sgid,\scid,\dattrs) \rbrace)$}{%
          \pcif \uid \notin \CU: \pcreturn \bot \\
          \pcif \gid \notin \HI: \pcreturn \bot \\
          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
          \pcif \exists \cid \in \scid~\st~\CRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cdot, \utrans \rangle \gets
          \langle \adv, %
          \Issue(\PRVIK[\gid],\PUBUK[\uid],(\GK[\gid],\dattrs)) \rangle \\
          \trans[\cid] \gets \utrans \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid, \bot, \dattrs) \\
          \pcreturn \top \\          
        }

        \procedure{$\OBTISS(\cid,\uid,\gid,
          \lbrace (\sgpk,\scid,\uattrs,\dattrs) \rbrace)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \gid \notin \HI: \pcreturn \bot \\          
          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
          \pcif \exists \cid \in \scid~\st~\CRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cred, \utrans \rangle \gets
          \langle \Obtain(\gpk,\PRVUK[\uid],\attrs), \\
          \pcind \pcind \pcind \pcind \pcind \pcind
          \Issue(\gpk,\isk,\PUBUK[\uid],\attrs) \rangle \\
          \trans[\cid] \gets \utrans;~\CRED[\cid] \gets \cred \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets \attrs \\
          \pcreturn \top \\
        }

        \procedure{$\OBTAIN(\cid,\uid,\gid,
          \lbrace (\sgpk,\scid,\uattrs,\dattrs) \rbrace)$}{%
          \pcif \uid \in \CU \lor \uid \notin \HU: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cred, \cdot \rangle \gets
          \langle \Obtain(\gpk,\PRVUK[\uid],\attrs),\adv \rangle \\
          \CRED[\cid] \gets \cred \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets \attrs \\
          \pcreturn \top \\
        }

@@

        \procedure{$\HOGEN(\gid,\feval,\finsp)$}{%
          \pcif \gid \in \HO \lor \gid \in \CO: \pcreturn \bot \\
          (\opk,\osk) \gets \OKeyGen(\parm) \\
          \OK[\gid] \gets (\opk,\osk,\feval,\finsp);
          \HO \gets \HO \cup \lbrace  \gid \rbrace \\
          \pcreturn \opk \\
        }

        \procedure{$\COGEN(\gid,\opk,\feval,\finsp)$}{%
          \pcif \gid \in \CO: \pcreturn \bot \\
          \CO \gets \CO \cup \lbrace \gid \rbrace \\          
          \pcif \gid \in \HO: \\
          \pcind \HO \gets \HO \setminus \lbrace \gid \rbrace; \\
          \pcind \pcreturn \OK[\gid]) \\
          \pcelse: \OK[\gid] = (\opk,\bot,\feval,\finsp) \\
          \pcreturn \top \\
        }

        \procedure{$\CUGEN(\uid,\upk)$}{%
          \pcif \uid \in \CU: \pcreturn \bot \\
          \CU \gets \CU \cup \lbrace \uid \rbrace \\          
          \pcif \uid \in \HU: \\
          \pcind \HU \gets \HU \setminus \lbrace \uid \rbrace; \\
          \pcind \pcreturn (\UK[\uid],\CRED[\uid]) \\
          \pcelse: \UK[\uid] = (\upk,\bot) \\          
          \pcreturn \top \\
        }

        \procedure{$\SIGN(\msg,
          \lbrace (\scid,\uattrs,\dattrs) \rbrace )$}{%
          \uid \gets \OWNR[\cid] \\
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \cred \gets \CRED[\cid] \\
          \sig \gets \Sign(\gpk,\PRVUK[\uid],\cred,\dattrs,\msg) \\
          \SIG[\cid] \gets \SIG[\cid] \cup \lbrace (\sig,\dattrs,\msg) \rbrace \\
          \pcreturn \sig \\
        }

        \procedure{$\OPEN(\sig)$}{%
          \textrm{Let}~\cid~\textrm{be s.t.}~(\sig,\dattrs,\msg) \in \SIG[\cid] \\
          \pcif \textrm{no such \cid exists, or there is more than one}: \\
          \pcind \pcreturn \bot \\
          \pcif \sig \in \CSIG: \pcreturn \bot \\
          (\upk,\cred,\oproof) \gets \Open(\gpk,\osk,\trans[\cid],\sig,\dattrs,\msg) \\
%          \OSIG \gets \OSIG \cup \lbrace (\sig,\upk,\cred) \rbrace \\
%          \CCRED \gets \CCRED \cup \lbrace \cid \rbrace \\
          \pcreturn (\upk,\cred,\oproof) \\
        }

        \procedure{$\CHALb(\msg,
          \lbrace (\cscid_0,\cscid_1,\uattrs,\dattrs) \rbrace )$}{%
          \pcif \ATTR[\cscid_0] \cap \ATTR[\cscid_1] \nsubseteq \dattrs:
          \pcreturn \bot \\
          \pcif \cuid_0 \neq \bot \lor \cuid_1 \neq \bot: \pcreturn \bot \\
          \cuid_0 = \OWNR[\ccid_0];~\cuid_1 = \OWNR[\ccid_1] \\
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
 %         \pcif \ccid_0 \in \CCRED \lor \ccid_1 \in \CCRED: \pcreturn \bot \\
          \csig \gets \Sign(\gpk,\PRVUK[\cuid_b],\CRED[\ccid_b],
          \dattrs,\msg) \\
          \CSIG \gets \CSIG \cup \lbrace \csig \rbrace \\
          \pcreturn \csig
        }

@@

    \caption{Detailed oracles available in our model.}
    \label{fig:oracles}
  \end{figure*}
}

>>>>

  \Obtain(\usk,\uattrs,\dattrs,\ldblbrace (gpk_i,\cred_i,\tuattrs_i,\tdattrs_i)\rdblbrace_{i \in \Issuers}),
  \Issue(\isk,\upk,\dattrs,\ldblbrace (\gpk_i,\tdattrs_i)\rdblbrace_{i \in \Issuers})

@@

  the ones in the $\tuattrs_i$'s) are kept hidden from the issuer, while those
  in \dattrs (as well as those in the $\tdattrs_i$'s) are revealed. Moreover,
  $\uattrs \cup \dattrs$ must be a subset of $\bigcup_i (\tuattrs_i \cup
  \tdattrs_i)$. In order to get the credential, the user may leverage previously

@@

  undisclosed attributes $\tuattrs_i$. The user outputs the produced credential
  \cred, while the issuer outputs the protocol transcript \utrans for the
  produced credential.
\item[$\sig \gets \Sign(\usk,\msg,\uattrs,\dattrs,
  \ldblbrace (\gpk_i,\cred_i,\tuattrs_i,\tdattrs_i)\rdblbrace_{i \in \Issuers})$.]

@@

  $\bigcup_i \uattrs_i$, which must be a subset of the corresponding disclosed
  (resp. undisclosed) attributes \tdattrs (resp. \tuattrs) in the credentials
  used to generate the signature.

@@

  \Verify(\sig,\msg,\dattrs, \ldblbrace \gpk_i \rdblbrace_{i \in \Issuers})$.]

@@

  arbitrary claims over disclosed attributes $\dattrs$, as well as

@@

  \Inspect(\osk,\trans,\sig,\msg,\dattrs,
  \ldblbrace \gpk_i \rdblbrace_{i \in \Issuers})$.] %
  \commentwho{Jesus}{I do not like this description. It's complicated. This needs

@@

  disclosed attributes $\dattrs$, as well as potentially undisclosed

@@

  If \trans is a valid set of transcripts of the execution of a

@@

  the credential associated to the inspector's group%
  \footnote{Note: we are not constraining that the group to which the inspector
    with key \osk belongs to, issued only one of the credentials used to
    generate the signature being inspected.}, then the function outputs

@@

\item[$1/0 \gets \Judge(\y,\iproof,\sig,\msg,\dattrs,
  \ldblbrace \gpk_i\rdblbrace_{i \in \Issuers})$.] %

@@

\paragraph{Oracles.} %
Oracles are the interface of the adversary with the corresponding games. In
other words: through these oracles, the game environment exposes to the adversary
functionality that could otherwise be executed only by honest parties with
private knowledge -- knowledge that would make the adversary capable of
trivially breaking the security properties formalized in the experiments.
In the game-based definitions of our \GSAC model, we leverage the following
oracles, which are formally defined in \figref{fig:oracles1} and
\figref{fig:oracles2}. Note that we identify issuers and inspectors by the group
identifier.

@@

        \procedure{$\HIGEN(\gid,\fissue)$}{%
          \pcif \gid \in \HI \lor \gid \in \CI: \pcreturn \bot \\
          (\ipk,\isk) \gets \IKeyGen(\parm) \\
          \IK[\gid] \gets (\ipk,\isk,\fissue) \\
          \HI \gets \HI \cup \lbrace \gid \rbrace \\
          \GK[\gid] \gets (\ipk,\fissue,\cdot,\cdot,\cdot) \\
          \pcreturn \ipk \\
        }

        \procedure{$\CIGEN(\gid,\ipk,\fissue)$}{%
          \pcif \gid \in \CI: \pcreturn \bot \\
          \CI \gets \CI \cup \lbrace \gid \rbrace \\          
          \pcif \gid \in \HI: \\
          \pcind \HI \gets \HI \setminus \lbrace \gid \rbrace; \\
          \pcind \pcreturn \IK[\gid] \\
          \pcelse: \IK[\gid] = (\ipk,\bot,\fissue) \\ 
          \GK[\gid] \gets (\ipk,\fissue,\cdot,\cdot,\cdot) \\         
          \pcreturn \top \\
        }

        \procedure{$\HUGEN(\uid)$}{%
          \pcif \uid \in \HU \lor \uid \in \CU: \pcreturn \bot \\
          (\upk,\usk) \gets \UKeyGen(\parm) \\
          \UK[\uid] \gets (\upk,\usk);
          \HU \gets \HU \cup \lbrace  \uid \rbrace \\
          \pcreturn \top
        }

@@

        \procedure{$\HOGEN(\gid,\feval,\finsp)$}{%
          \pcif \gid \in \HO \lor \gid \in \CO: \pcreturn \bot \\
          (\opk,\osk) \gets \OKeyGen(\parm) \\
          \OK[\gid] \gets (\opk,\osk,\feval,\finsp) \\
          \HO \gets \HO \cup \lbrace  \gid \rbrace \\
          \GK[\gid] \gets (\cdot,\cdot,\opk,\feval,\finsp) \\          
          \pcreturn \opk \\
        }

        \procedure{$\COGEN(\gid,\opk,\feval,\finsp)$}{%
          \pcif \gid \in \CO: \pcreturn \bot \\
          \CO \gets \CO \cup \lbrace \gid \rbrace \\          
          \pcif \gid \in \HO: \\
          \pcind \HO \gets \HO \setminus \lbrace \gid \rbrace; \\
          \pcind \pcreturn \OK[\gid]) \\
          \pcelse: \OK[\gid] = (\opk,\bot,\feval,\finsp) \\
          \GK[\gid] \gets (\cdot,\cdot,\opk,\feval,\finsp) \\
          \pcreturn \top \\
        }

        \procedure{$\CUGEN(\uid,\upk)$}{%
          \pcif \uid \in \CU: \pcreturn \bot \\
          \CU \gets \CU \cup \lbrace \uid \rbrace \\          
          \pcif \uid \in \HU: \\
          \pcind \HU \gets \HU \setminus \lbrace \uid \rbrace; \\
          \pcind \pcreturn (\UK[\uid],\CRED[\uid]) \\
          \pcelse: \UK[\uid] = (\upk,\bot) \\          
          \pcreturn \top
        }

@@

    \caption{Detailed oracles available in our model (1/2). Oracles for
      generating users, issuers, and inspectors.\\
      \doubt{Do we need to specify the functions in the GEN Oracles? They do
        not seem necessary in \SIGN/\CHALb/\INSPECT. Should they? Maybe there
        is something wrong here... Maybe they are needed in the games...}}
    \label{fig:oracles1}
  \end{figure*}
}

        \procedure{$\ISSUE(\cid,\uid,\gid,\dattrs,
          \ldblbrace (\sgid,\scid,\tdattrs) \rdblbrace)$}{%
          \pcif \uid \notin \CU: \pcreturn \bot \\
          \pcif \gid \notin \HI: \pcreturn \bot \\
%          \pcif \exists \cid
          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot: \pcreturn \bot \\
          \langle \cdot, \utrans \rangle \gets
          \langle \adv, \\
          \pcind \pcind
          \Issue(\PRVIK[\gid],\PUBUK[\uid],
          \ldblbrace (\GK[\sgid],\tdattrs)\rdblbrace) \rangle \\
          \trans[\cid] \gets \utrans \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid, \bot, \dattrs) \\
          \pcreturn \top \\          
        }

        \procedure{$\OBTAIN(\cid,\uid,\gid,\uattrs,\dattrs,
          \ldblbrace (\sgid,\scid,\tuattrs,\tdattrs) \rdblbrace)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot: \pcreturn \bot \\
          \langle \cred, \cdot \rangle \gets
          \langle \Obtain(\PRVUK[\uid],\uattrs,\dattrs, \\
          \hspace*{65pt}
          \ldblbrace (\GK[\sgid],\CRED[\scid],\tuattrs,\tdattrs) \rdblbrace), \\
          \hspace*{50pt} \adv \rangle \\
          \CRED[\cid] \gets \cred \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid, \uattrs, \dattrs) \\
          \pcreturn \top \\
        }

        \procedure{$\INSPECT(\gid,\sig,\msg)$}{%
          \textrm{Let}~\uid~\textrm{be s.t.}~(\sig,\msg,\scid,\uattrs,\dattrs,\sgid)
          \in \SIG[\uid] \\
          \pcif \sig \in \CSIG: \pcreturn \bot \\
          (\y,\oproof) \gets
          \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,\GK[\sgid]) \\
          \pcreturn (\y,\oproof)
        }

        \procedure{$\OBTISS(\cid,\uid,\gid,\uattrs,\dattrs,
          \ldblbrace (\sgid,\scid,\tuattrs,\tdattrs) \rdblbrace)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \gid \notin \HI: \pcreturn \bot \\          
          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot:
          \pcreturn \bot \\
          \langle \cred, \utrans \rangle \gets
          \langle \Obtain(\PRVUK[\uid],\uattrs,\dattrs,\ldblbrace (\GK[\sgid],
          \CRED[\scid],\tuattrs,\tdattrs) \rdblbrace), \\
          \pcind \pcind \pcind \pcind \pcind \pcind
          \Issue(\PRVIK[\gid],\PUBUK[\uid],\ldblbrace (\GK[\sgid],\tdattrs)
          \rdblbrace ) \rangle \\
          \trans[\cid] \gets \utrans;~\CRED[\cid] \gets \cred \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid,\uattrs,\dattrs) \\
          \pcreturn \top \\
        }

        \procedure{$\SIGN(\msg,\uid,\uattrs,\dattrs,
          \ldblbrace (\sgid,\scid,\tuattrs,\tdattrs) \rdblbrace )$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \cred \gets \CRED[\cid] \\
          \sig \gets \Sign(\PRVUK[\uid],\msg,\uattrs,\dattrs,
          \ldblbrace (\GK[\sgid],\CRED[\scid],\tuattrs,\tdattrs) \rdblbrace) \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\sig,\msg,\scid,\uattrs,\dattrs,\sgid) \rbrace \\
          \pcreturn \sig \\
        }

        \procedure{$\CHALb(\msg,
          (\uid_{0,1},\uattrs_{0,1},\dattrs_{0,1},\ldblbrace (\sgid,\cscid_{0,1},\tuattrs_{0,1},\tdattrs_{0,1}) \rdblbrace))$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pccomment{Note: since both \uid's need to be honest, we must have
            all the}\\
          \pccomment{undisclosed attributes in the \ATTR lists.} \\
          \dattrs' \gets \DATTR[\cscid_0] \cap \DATTR[\cscid_1] \\
          \uattrs' \gets \UATTR[\cscid_0] \cap \UATTR[\cscid_1] \\
          \pcif (\dattrs_0 \cap \dattrs_1) \nsubseteq \dattrs':
          \pcreturn \bot \\
          \pcif (\uattrs_0 \cap \uattrs_1) \nsubseteq \uattrs':          
          \pcreturn \bot \\
          \csig \gets \Sign(\PRVUK[\uid_b],\msg,\uattrs_b,\dattrs_b,
          \ldblbrace (\GK[\sgid],\CRED[\scid_b],\tuattrs_b,\tdattrs_b) \rdblbrace) \\
          \CSIG \gets \CSIG \cup
          \lbrace (\csig,\msg,\scid_b,\uattrs_b,\dattrs_b,\sgid) \rbrace \\
          \pcreturn \csig
        }

    \caption{Detailed oracles available in our model (2/2). Oracles for
      obtaining credentials, signatures, and processing them.}
    \label{fig:oracles}
  \end{figure*}
}
